A Catalogue of Twists of Supersymmetric Gauge Theories

### 2020-01-23 paper.tex
4d N=1 update

\begin{thm}
The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1] \map(L\times (N_\RR)_{\mr{dR}}, B\fg)$ \brian{the $B$-direction was missing}. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:8dBFreduction}
\end{thm}
\begin{proof}
By Theorem \ref{thm:8dholomorphictwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory. Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant. By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $\map(L\times N_\RR, T^*[3] B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

@@

\begin{align*}
S_{\gauge} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}

@@

The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional spin representations of $\Spin(4, \CC)\cong \SU(2) \times \SU(2)$ and $W$ is a complex vector space. 
We have isomorphisms $S_\pm \cong S_\pm^*$ which equivalently determine equivariant pairings $S_\pm \otimes S_\pm \to \CC$.

@@

\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang-Mills theory} \label{4d_1_section}
We consider $\cN=1$ supersymmetric Yang-Mills for a Lie algebra $\fg$ coupled to supersymmetric matter.
The matter consists of the $\cN=1$ chiral multiplet valued in a complex representation $R$.

The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall. 
Let $\fg$ be a complex Lie algebra equipped with a symmetric bilinear invariant nondegenerate pairing and $R$ a complex $\fg$-representation. 
We consider $\cN=1$ super Yang--Mills theory on $M=\RR^6$ with the Euclidean metric. 
We fix $W=\CC$. 
The theory admits an $R$-symmetry group $G_R=\U(1)$.

The field content for the 4-dimensional $\cN=1$ super Yang-Mills theory coupled to chiral matter is given by:
\begin{itemize}
\item $\fg$-valued bosons: a gauge field $A \in \Omega^1(\RR^4 ; \fg)$.
\item $R$-valued bosons: $(\Bar{\phi}, \phi) \in C^\infty(\RR^4 ; R \oplus R^*)$.
\item $\fg$-valued fermions: $(\lambda_+, \lambda_-) \in \Omega^0(\RR^4 ; S_+ \otimes \fg \oplus S_- \otimes \fg)$.
\item $R$-valued fermions: $(\psi_-,\psi_+) \in C^\infty(\RR^4 ; S_+ \otimes R \oplus \otimes S_- \otimes R^*)$.
\end{itemize}

This theory admits a unique twist, which is necessarily of rank $1$:
\begin{itemize}
\item A square-zero supercharge $Q\neq 0\in\Sigma$ has 2 invariant directions, so it gives rise to a holomorphic theory. 
The identity homomorphism $\alpha = {\rm id} \colon \U(1) \cong G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory. 
Such a supercharge is stabilized by $\SU(2)$. 
Also, we have a compatible twisting homomorphism 
\[
\phi : \MU(2) \to {\rm Spin}(4) \times U(1) 
\]
where on the first component is the map $\MU(2) \to {\rm Spin}(4)$ lifting $\U(2) \to \SO(4)$ and on the second component $\det^{1/2} : \MU(2) \to U(1)$ is the square root of determinant. 
\end{itemize}

%The spinorial pairing $(-,-) : S_\pm \otimes S_\pm \to \CC$ induces a pairing between $S_\pm \otimes R$ and $S_{\pm} \otimes R^*$ that we also denote by $(-,-)_R$.

@@

For concreteness, we will fix a square-zero supercharge of positive chirality
\[
Q = Q_+ \in S_+ \otimes W
\]
to twist by. 
The data of such a $Q_+$ is equivalent to the data of a K\"{a}hler structure $L$ on $V_\RR$.

Under the embedding $\MU(L) = \MU(2) \subset \Spin(\VV_\RR)$, the spin representations decompose as
\[
S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2} \;\; , \;\; S_- = L \otimes \det(L)^{-1/2} .
\]

We consider the twisting homomorphism
\[
\phi = \det \, ^{1/2} : \MU(2) \to \U(1)
\]
for which $Q_+$ becomes a scalar.
Under this twisting homomorphism, we have an $\MU(2)$-identification $W = \det(L)^{1/2}$. 
By construction, $Q_+$ lies in the first factor of $S_+ \otimes W = \CC \oplus \det(L)$.

Since we have an isomorphism $\alpha : U(1) \cong G_R$ the twisted theory is $\ZZ$-graded.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
The fields decompose as:
\[
\begin{array} {lllcccccc}
& &  & {\rm Untwisted} & R & {\rm Twisted}  \\
c & \mapsto & A_{0} \in \Omega^0(\CC^2 ; \fg) & -1 & 0 & -1 \\
A & \mapsto & A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) & 0 & 0 & 0 \\
\lambda_- & \mapsto & \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) & 0 & -1 & -1 \\
\lambda_+ & \mapsto & \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) & 0 & +1 & + 1 \\
\phi & \mapsto & \phi \in \Omega^0 (\CC^2 ; R^*) & 0 & 0 & 0 \\
\Bar{\phi} & \mapsto & \gamma_0 \in \Omega^{0,0}(\CC^2 ; R) & 0 & 0 & 0 \\
\psi_+ & \mapsto & \psi_0 + \beta_{2,0} \in \Omega^{0}(\CC^2 ; R^*) \oplus \Omega^{2,0}(\CC^2 ; R^*) & 0 & -1 & -1 \\
\psi_- & \mapsto & \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) & 0 & +1 & +1 
\end{array}
\]
The anti-fields decompose similarly. 
%\brian{Is it necessary to put in the antifields?} 
%and their antifields:
%\begin{align*}
%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
%A^* & \mapsto B_{2,1} + A^*_{1,0} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
%\lambda^*_- & \mapsto \lambda_{1,0}^* \in \Omega^{1,2}(\CC^2 ; \fg) \\
%\lambda^*_+ & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) \\
%\phi^* & \mapsto \phi^* \in \Omega^{2,2}(\CC^2 ; R^*) \\
%\Bar{\phi}^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R) \\
%\psi^*_+ & \mapsto \psi_{2,2}^* + \gamma_{0,2} \in \Omega^{2,2}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) \\
%\psi^*_- & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R)
%\end{align*}

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form, $\Omega\in\Omega^{2, 0}(M)$ the holomorphic volume form and $\ol{\Omega}\in\Omega^{0, 2}(M)$ the antiholomorphic volume form.  We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^2}{2} = \Omega\wedge \ol{\Omega}.\]

@@

\begin{align*}
S_{\mr{gauge}} &= \int \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left(\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \bigg( ((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0\wedge B_{2,1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* +B_{2,1} \wedge [A_0, A_{0,1}] + A_{1,0}^* \wedge [A_{0}, A_{1,0}] \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \\
I^{(1)}_{\mr{gauge}} &=  \int  \left( - (\lambda_{1,0}, A_{0,1}^*) + \frac 12 (F_{0,2},B_{2,0}) + \frac 12 (F_{1,1}, \lambda_0^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int  \left( (\phi, \psi_0^*) + \frac 12( \ol \dd_{A_{0,1}} \gamma_{0}, \beta_{2,1}) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int  (\lambda_0^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^2}2$.

@@

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ is $\U(2)$-equivariantly equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$, with classical moduli space $T^*[-1]\mr{Map}(\CC^2, R/\gg)$. 
\end{thm}

\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we integrate out the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int  (\lambda_{1,0} , A_{0,1}^*)$ and  $\int (\phi, \psi_{1,1}^*)$.  
Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form BRST doublets, 
which can be integrated out using Proposition \ref{prop:BRSTdoublet}.

@@

%\begin{itemize}
%\item[(1)] 
%We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
%The fields of the pure Yang-Mills part decomposes as:
%\begin{align*}
%c & \mapsto A_{0} \in \Omega^0(\CC^2 ; \fg) \\
%A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
%\lambda_+ & \mapsto \lambda_{1,0} \in \Omega^{1,0}(\CC^2 ; \fg) \\
%\lambda_- & \mapsto \lambda_0 + A_{0,2} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg) 
%\end{align*}
%and their antifields:
%\begin{align*}
%c^* & \mapsto B_{2,2} \in \Omega^{2,2}(\CC^2 ; \fg) \\
%A^* & \mapsto B_{2,1} + B_{1,2} \in \Omega^{2,1}(\CC^2;\fg) \oplus \Omega^{1,2}(\CC^2; \fg) \\
%\lambda^*_+ & \mapsto \lambda_{1,2} \in \Omega^{1,2}(\CC^2 ; \fg) \\
%\lambda^*_- & \mapsto \lambda_0^*+ B_{2,0} \in \Omega^{0}(\CC^2 ; \fg) \oplus \Omega^{2,0}(\CC^2 ; \fg) 
%\end{align*}
%
%The matter fields decompose as
%\begin{align*}
%\phi & \mapsto \gamma_0 \in \Omega^0 (\CC^2 ; R) \\
%\Bar{\phi} & \mapsto \Bar{\phi} \in \Omega^{2,2}(\CC^2 ; R^*) \\
%\psi_+ & \mapsto \gamma_{0,1} \in \Omega^{0,1}(\CC^2 ; R) \\
%\psi_- & \mapsto \beta_{2,0} + \Tilde{\beta}_{2,2} \in \Omega^{2,0}(\CC^2 ; R^*) \oplus \Omega^{2,2}(\CC^2 ; R^*) 
%\end{align*}
%and their antifields:
%\begin{align*}
%\phi^* & \mapsto \beta_{2,2} \in \Omega^{2,2} (\CC^2 ; R^*) \\
%\Bar{\phi}^* & \mapsto \Bar{\phi}^* \in \Omega^{0,0}(\CC^2 ; R) \\
%\psi^*_+ & \mapsto \beta_{2,1} \in \Omega^{2,1}(\CC^2 ; R^*) \\
%\psi^*_- & \mapsto \Tilde{\gamma}_0 + \gamma_{0,2} \in \Omega^{0,0}(\CC^2 ; R) \oplus \Omega^{0,2}(\CC^2 ; R) 
%\end{align*}
%
%\item[(2)] Next, we study the linear differential in the twisted theory. 
%At the linear level, the matter and gauge sectors completely decouple. 
%
%For the gauge sector, the linear differential on the twisted BV complex is the following:
%\[
%\xymatrix{
%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
%\Omega^0(\CC^2; \fg)_{A_0} \ar[r]^-{\dbar} & \Omega^{0,1}(\CC^2; \fg)_{A_{0,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{A_{0,2} } &  \\
%& \Omega^{2,0}(\CC^2; \fg)_{B_{2,0}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,1}(\CC^2; \fg)_{B_{2,1}} \ar[r] & \Omega^{2,2}(\CC^2 , \fg)_{B_{2,2}} \\
%\Omega^{1,0} (\CC^2; \fg)_{\lambda_{1,0}} \ar@{.>}[r]^-{=} & \Omega^{1,0}(\CC^2; \fg)_{A_{1,0}} & \Omega^{2,1}(\CC^2; \fg)_{B_{1,2}} \ar@{.>}[r]^-{=} & \Omega^{2,1}(\CC^2; \fg)_{\lambda_{1,2}} \\
%& \Omega^0(\CC^2 ; \fg)_{\lambda_0^*} \ar@{.>}[r]^-{=} & \Omega^0(\CC^2 ; \fg)_{\lambda_0} & 
%}
%\]
%The solid arrows represent the piece of the linear differential coming from the original linear BV differential of the untwisted theory.
%The dotted arrows represent the piece of the linear differential which depends on the supercharge $Q = Q_-$ we are twisting by. 
%This complex is equivalent to the linearized piece holomorphic BF theory on $\CC^2_{\dbar}$ with values in $\fg$. 
%
%For the matter sector, the linear differential is:
%\[
%\xymatrix{
%\ul{-1} & \ul{0} & \ul{1} & \ul{2} \\
%& \Omega^0(\CC^2; R)_{\gamma_0} \ar@{.>}[r]^-{\dbar} & \Omega^{0,1}(\CC^2; R)_{\gamma_{0,1}} \ar[r]^-{\dbar} & \Omega^{0,2}(\CC^2; R)_{\gamma_{0,2} } \\
%\Omega^0(\CC^2; R^*)_{\beta_{2,0}} \ar[r]^-{\dbar} & \Omega^{2,1}(\CC^2; R^*)_{\beta_{2,1}} \ar@{.>}[r]^-{\dbar} & \Omega^{2,2}(\CC^2 , R^*)_{\beta_{2,2}} \\
%\Omega^{2,2} (\CC^2; R^*)_{\Tilde{\beta}_{2,2}} \ar@{.>}[r]^-{=}& \Omega^{2,2}(\CC^2; R^*)_{\Bar{\phi}} & \Omega^{0,0}(\CC^2; R)_{\Bar{\phi}^*} \ar@{.>}[r]^-{=} & \Omega^{0,0}(\CC^2; R)_{\Tilde{\gamma}_0}
%}
%\]
%This complex is equivalent to the holomorphic $\beta\gamma$ system on $\CC^2_{\dbar}$ with values in $R$. 
%
%\item[(3)] 
%We now observe that the interacting parts of the twisted theory agree with the interactions of holomorphic BF theory coupled to the $\beta\gamma$ system. 
%\end{itemize}

>>>>

\begin{thm}
The twist of $(4+\dim(L))$-dimensional super Yang--Mills on $L\times N_\RR$ by $Q$ is perturbatively equivalent to the generalized BF theory with the space of fields $\map(L\times (N_\RR)_{\mr{dR}}, T^*[3] B\fg)$. Moreover, the equivalence is $\MU(L)\times \Spin(N_\RR)$-equivariant.
\label{thm:8dBFreduction}
\end{thm}
\begin{proof}
By Theorem \ref{thm:8dholomorphictwist} the twist of 8d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory. Moreover, the equivalence is $\MU(L)\times \SU(N)$-equivariant. By Corollary \ref{cor:BFholomorphicreduction} we get that the dimensional reduction of holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized BF theory with the space of fields $\map(L\times N_\RR, T^*[3] B\fg)$ and this isomorphism is $\MU(L)\times \SO(N_\RR)$-equivariant, where $\SO(N_\RR)$ acts on $N$ via the homomorphism \eqref{eq:SOtoSU}.
\end{proof}

@@

\begin{align*}
S_{\gauge} &= \int \dvol \left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(B \wedge \dd_{A_{1,0}} \rho) + \omega^2\chi\Lambda(\ol \dd_{A_{0,1}} \rho) - \omega(\rho \wedge \dd_{A_{1,0}} B) + \xi \ol \dd_{A_{0,1}} B \right)  \\
S_{\matter} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \phi) + (\dd_{A_{1,0}}\phi, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2\wedge(\wt\nu \ol \dd_{A_{1,0}} \psi) + \psi \wedge \ol \dd_{A_{0,1}} \psi + \\
&\qquad + 2\dvol(([\xi,\nu],\wt\nu) + ([\chi, \phi], \wt\nu) )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} c \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} c\wedge A_{0, 1}^* + [B, c]\wedge B^* +  [\xi, c]\wedge \xi^* + [\chi, c]\chi^* +[\rho, c]\wedge \rho^* + \\
&\qquad + \frac{1}{2}[c, c]c^* + [\nu, c]\wedge \nu^* + [\phi, c]\wedge \phi^* + [\psi, c]\wedge \psi^* + [\wt\nu, c]\wedge \wt\nu^* \\
I^{(1)}_{\gauge} &=  \int \dvol \left( - (\rho, A_{1,0}^*) + \frac 12 (F_{0,2},B^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\matter} &=  \int \dvol \left( (\wt\nu, \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \phi, \psi^*) \right)\\
I^{(2)}_{\gauge} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}

@@

The 4-dimensional supersymmetry algebra has odd part $\Sigma\cong S_+\otimes W\oplus S_-\otimes W^*$, where $S_+, S_-$ are the 2-dimensional semi-spin representations of $\Spin(4, \CC)\cong \SL(2, \CC) \times \SL(2, \CC)$ and $W$ is a complex vector space. The semi-spin representations carry symplectic pairings $S_\pm\otimes S_\pm\rightarrow \CC$.

@@

\subsection{\texorpdfstring{$\cN=1$}{N=1} Super Yang--Mills} \label{4d_1_section}
The general setup for $\cN=1$ super Yang--Mills is described in Section \ref{sec:SYM} which we now recall.  Let $R$ be a complex $\fg$-representation. We consider $\cN=1$ super Yang--Mills theory on $M=\RR^4$ with the Euclidean metric. The theory admits an $R$-symmetry group $G_R=\U(1)$ which acts on $W=\CC$ with weight $1$.

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge field $A \in \Omega^1(M; \fg)$.
\item Gauge fermions $(\lambda_+, \lambda_-) \in \Omega^0(M; \Pi S_+ \otimes \fg \oplus \Pi S_- \otimes \fg)$.
\item Matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(M; R \oplus R^*)$.
\item Matter fermions $(\psi_-,\psi_+) \in \Omega^0(M; \Pi S_+ \otimes R^* \oplus \Pi S_- \otimes R)$.
\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
\end{itemize}

The $R$-symmetry acts with weight $\pm 1$ on $\lambda_\pm, \psi_\pm$.

The theory admits a unique twist:
\begin{itemize}
\item Elements $Q\in S_+\oplus S_-$ of rank $(1, 0)$ or rank $(0, 1)$. Such supercharges are automatically square-zero and are holomorphic. The identity homomorphism $\alpha = {\rm id} \colon \U(1) \cong G_R$ makes $Q$ weight $+1$, so in this case we get a $\ZZ$-grading on the twisted theory. Also, we have a compatible twisting homomorphism $\phi\colon \MU(2)\xrightarrow{\det^{1/2}}\U(1)$.
\end{itemize}

@@

Choose a complex structure $L$ on $V_\RR$. Under the embedding $\MU(L) = \MU(2) \subset \Spin(V_\RR)$, the semi-spin representations decompose as
\[
S_+ = \det(L)^{-1/2} \oplus \det(L)^{1/2},\qquad S_- = L \otimes \det(L)^{-1/2} .
\]
Consider the twisting homomorphism $\phi\colon\MU(2)\rightarrow G_R$ under which $W = \det(L)^{-1/2}$. Then the spinorial representation becomes
\[\Sigma = (\CC Q\oplus \det(L)^{-1})\oplus L.\]

The identity map $\alpha\colon \U(1)\cong G_R$ makes $Q$ weight $1$.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to $\MU(2)$.
\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge fields $A_{1, 0} \in \Omega^{1, 0}(M; \fg)$, $A_{0, 1}\in\Omega^{0, 1}(M; \fg)$.
\item Gauge fermions $\lambda_{1, 0}\in\Omega^{1, 0}(M; \fg)[1]$, $\lambda_0\in\Omega^0(M; \fg)[-1]$, $A_{0, 2}\in\Omega^{0, 2}(M; \fg)[-1]$.
\item Matter bosons $\phi\in\Omega^0(M; R^*)$, $\gamma_0\in\Omega^0(M; R)$.
\item Matter fermions $\psi_0\in\Omega^0(M; R^*)[1]$, $\beta_{2, 0}\in\Omega^{2, 0}(M; R^*)[1]$, $\gamma_{0, 1}\in\Omega^{0, 1}(M; R)[-1]$.
\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
\end{itemize}
The corresponding antifields are given by:
\begin{itemize}
\item $A_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-1]$, $B_{2, 1}\in\Omega^{2, 1}(M; \fg)[-1]$.
\item $\lambda_{1, 0}^*\in\Omega^{1, 2}(M; \fg)[-2]$, $\lambda_0^*\in\Omega^0(M; \fg)$, $B_{2, 0}\in\Omega^{2, 0}(M; \fg)$.
\item $\phi^*\in\Omega^{2, 2}(M; R)$, $\gamma_0^*\in\Omega^0(M; R^*)$.
\item $\psi_0^*\in\Omega^{2, 2}(M; R)[-2]$, $\gamma_{0, 2}\in\Omega^{0, 2}(M; R)[-2]$, $\beta_{2, 1}\in\Omega^{2, 1}(M; R^*)$.
\item $B_{2, 2}\in\Omega^{2, 2}(M; \gg)[-2]$.
\end{itemize}

Let $\omega\in\Omega^{1, 1}(M)$ be the K\"ahler form. We denote the real volume form on $M$ by
\[\dvol = \frac{\omega^2}{2}.\]

@@

\begin{align*}
S_{\mr{gauge}} &= \int\dvol\left(-(F_{2, 0}, F_{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \frac 12 \left((\lambda_{1,0} \wedge \dd_{A_{1,0}} A_{0,2}) + \omega (\lambda_{1,0} \wedge \dbar_{A_{0,1}} \lambda_0) \right)  \\
S_{\mr{matter}} &= \int \dvol \left((\dd_{A_{1,0}}\phi , \ol \dd_{A_{0,1}} \gamma_0) + (\dd_{A_{1,0}}\gamma_0, \ol \dd_{A_{0,1}} \phi)\right) + \omega (\psi_0 \partial_{A_{1,0}} \gamma_{0,1}) + \beta_{2,0} \dbar_{A_{0,1}} \gamma_{0,1}  + \\
&\qquad + 2 (\omega \wedge ([\lambda_{1,0}, \gamma_{0,1}] ,\gamma_{0}) + ([A_{0,2}, \beta_{2,0}], \phi) )  \\
S_{\mr{anti}} &= \int \bigg(\dd_{A_{1, 0}} A_0 \wedge A_{1,0}^* + \ol\dd_{A_{0, 1}} A_0 \wedge B_{2, 1} + [\lambda_{1,0}, A_0]\wedge \lambda_{1,0}^* + \dvol ([\lambda_{0}, A_0], \lambda_{0}^*) + [A_0, A_{0,1}]\wedge B_{2, 1} + [A_{0}, A_{1,0}]\wedge A_{1, 0}^* \\
&\qquad + \frac{1}{2}[A_0, A_0]B_{2, 2} + [\phi, A_0] \phi^* + [\gamma_0, A_0] \beta_{2,2} + [\gamma_{0,1}, A_0]\wedge \beta_{2,1} + [\psi_0, A_0] \psi_0^* + [\beta_{2,0}, A_0] \wedge \gamma_{0,2} \bigg) \\
I^{(1)}_{\mr{gauge}} &=  \int  \left( - \lambda_{1,0}\wedge A_{1,0}^* + \frac 12 F_{0,2}\wedge B_{2,0} + \frac 12 \omega\wedge F_{1,1} \lambda_0^*  \right) \\
I^{(1)}_{\mr{matter}} &=  \int  \left( \psi_0 \phi^* + \frac 12 \ol \dd_{A_{0,1}} \gamma_{0}\wedge \beta_{2,1} \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol(\lambda_0^*)^2.
\end{align*}

@@

\begin{thm}[See also \cite{SWchar}] \label{4d_minimal_twist_thm}
The holomorphic twist of 4d $\cN=1$ super Yang--Mills with matter valued in a $\fg$representation-representation $R$ is perturbatively equivalent to holomorphic $BF$ theory with the space of fields $T^*[-1]\map(\CC^2, R/\fg)$. Moreover, the equivalence is $\U(2)$-equivariant.
\end{thm}

\begin{proof}
The proof of this theorem is very similar to the proof of Theorem \ref{thm:10dholomorphictwist}.  
First, we eliminate the fields $\lambda_0$ and $\lambda_0^*$ using Proposition \ref{prop:integrateoutfield}.  
We then observe that the action includes the terms $\int \lambda_{1,0} \wedge A_{1,0}^*$ and  $\int \psi_0\phi^*$. Thus, the two pairs $(\lambda_{1,0}, A_{1,0})$ and $(\phi, \psi_0)$ form trivial BRST doublets, which can be eliminated using Proposition \ref{prop:BRSTdoublet}.

@@

\subsection{\texorpdfstring{$\cN=2$}{N=2} Super Yang--Mills} \label{4d_2_section}

The 4d $\cN=2$ super Yang--Mills theory is obtained by a dimensional reduction from the 6d $\cN=(1, 0)$ super Yang--Mills theory with matter valued in a symplectic $\fg$-representation $U$. It admits the $R$-symmetry group $G_R=\SU(W)\times \U(1)$ with $W$ the two-dimensional representation on which $\U(1)$ acts with weight $1$.

\vspace{-10pt}
\paragraph{Fields:} The BRST fields are given by:
\begin{itemize}
\item Gauge field $A \in \Omega^1(M; \fg)$.
\item Scalar fields $a, \wt a\in\Omega^0(M;\fg)$.
\item Gauge fermions $(\lambda_+, \lambda_-) \in \Omega^0(M; \Pi S_+ \otimes W\otimes \fg \oplus \Pi S_- \otimes W^*\otimes \fg)$.
\item Matter boson $\phi\in\Omega^0(M; U\otimes W)$.
\item Matter fermions $(\psi_-, \psi_+)\in\Omega^0(M; \Pi S_+\otimes U\oplus \Pi S_-\otimes U)$.
\item A ghost field $A_0\in \Omega^0(M; \gg)[1]$.
\end{itemize}

$\U(1)\subset G_R$ has the following action: weight $2$ on $a$, weight $-2$ on $\wt a$ and weight $\pm 1$ on $\lambda_\pm,\psi_\pm$.

There are three classes of square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra, distinguished by the ranks of the two summands $(Q_+,Q_-) \in S_+ \otimes W \oplus S_- \otimes W^*$:
\begin{itemize}
 \item Rank $(1,0)$ and $(0,1)$ supercharges automatically square to zero.  
 The corresponding twists are holomorphic.
 Such twists factor through a copy of the $\cN = 1$ supersymmetry algebra. As before, they admit a $\ZZ$-grading and a twisting homomorphism from $\MU(2)$.
 \item Rank $(2,0)$ and $(0,2)$ supercharges also automatically square to zero. 
 The corresponding twists are topological (the \emph{Donaldson twist}). 
 \item Rank $(1,1)$ square-zero supercharges have three invariant directions.
\end{itemize}
